A Kochen-Specker system has at least 22 vertices

### 2014-04-08 main.tex
start of introduction§

% TODO whose idea is this orthogonality graph
TODO

>>>>

% TODO whose idea is this orthogonality graph
\subsection{The experiment}

Let's perform the following experiment.  Shoot a deuterium atom,
or any other spin-1 particle,
along, say: the x-axis, through a uniform magnetic field.

Depending on the direction of the magnetic field,
the particle will move undisturbed
or deviate.

Quantum Mechanics only predicts the chance, given the initial configuration
of the field, whether the particle will deviate.
Its probabilistic prediction has been thouroughly tested.
One could wonder: is there a deterministic theory.
